A Possibilistic Valid-time Model

### 2011-12-06 ipmu2012/ipmu.tex
Mr. T modifications.

\usepackage[dvips]{graphicx}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amsmath}
\usepackage{amsfonts}

\hyphenation{pro-per-ties}
\hyphenation{ge-ne-ral-ly}
\hyphenation{pre-fe-ren-ces}
\hyphenation{u-sing}
\hyphenation{pu-nish-ment}

@@

\mainmatter              % start of the contributions
%
\title{A possibilistic valid-time model}
%
%\titlerunning{A Fuzzy Valid-Time Model}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Jos\'e Enrique Pons \and Christophe Billiet \and Olga Pons Capote \and Guy de Tr\'e}
%Jeffrey Dean \and David Grove \and Craig Chambers \and Kim~B.~Bruce \and
%Elsa Bertino}
%
\authorrunning{Jos\'e Enrique Pons et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{
Department of Computer Science and Artificial Intelligence \\
Universidad de Granada \\
Escuela T\'ecnica Superior de Ingenier\'ia Inform\'atica \\
C/Periodista Daniel Saucedo Aranda s/n \\
E-18071 (Granada-Spain)\\
\email{jpons,opc@decsai.ugr.es}\\ 
%WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
%\and
%Universit\'{e} de Paris-Sud,
%Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
%F-91405 Orsay Cedex, France
\and 
Department of Telecommunications and Information Processing
Ghent University
Sint Pietersniewstraat 41 B-9000, Gent, Belgium.
\email{Christophe.Billiet,Guy.De.Tre@ugent.be}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

@@

%%%%%%%%%%%%%%%%
%
% FURTHER RESEARCH WORK
%
%%%%%%%%%%%%%%%
%
\section{Conclusions and further research work}
\label{sec:futher-research}
\input{conclusions}
%

>>>>

\usepackage[dvips]{graphicx}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{multirow}
\hyphenation{pro-per-ties}
\hyphenation{ge-ne-ral-ly}
\hyphenation{pre-fe-ren-ces}
\hyphenation{u-sing}
\hyphenation{pu-nish-ment}

@@

\mainmatter              % start of the contributions
%
\title{A Possibilistic Valid-time Model}
%
%\titlerunning{A Fuzzy Valid-Time Model}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Jos\'e Enrique Pons \and Christophe Billiet \and Olga Pons Capote \and Guy De Tr\'e}
%Jeffrey Dean \and David Grove \and Craig Chambers \and Kim~B.~Bruce \and
%Elsa Bertino}
%
\authorrunning{Jos\'e Enrique Pons et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{
Department of Computer Science and Artificial Intelligence \\
Universidad de Granada \\
Escuela T\'ecnica Superior de Ingenier\'ia Inform\'atica \\
C/Periodista Daniel Saucedo Aranda s/n \\
E-18071 (Granada-Spain)\\
\email{jpons,opc@decsai.ugr.es}\\ 
%WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
%\and
%Universit\'{e} de Paris-Sud,
%Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
%F-91405 Orsay Cedex, France
\and 
Department of Telecommunications and Information Processing
Ghent University
Sint Pietersnieuwstraat 41 B-9000, Ghent, Belgium.
\email{Christophe.Billiet,Guy.De.Tre@ugent.be}
}

\maketitle              % typeset the title of the contribution
\def\JPicScale{0.5}
\begin{abstract}

@@

%%%%%%%%%%%%%%%%
%
% FURTHER RESEARCH WORK
%
%%%%%%%%%%%%%%%
%
\section{Conclusions and Further Research}
\label{sec:futher-research}
\input{conclusions}
%
